---
title: "Visual Resume easel"
author: "Derek Sollberger"
date: "February 10, 2017"
output: html_document
---

The `VisualResume` package was written by Nathaniel Phillips and can be downloaded at his GitHub repository at https://github.com/ndphillips/VisualResume

## Installation

If needed, you may have to individually install the following six packages first before the installation of `VisualResume` was accepted (but the package dependencies should work now):

* coda
* gtools
* MatrixModels
* mvtnorm
* pbapply
* showtextdb

After that, the direct-from-GitHub installation worked as prescribed:
```{r, eval = FALSE}
#install.packages("devtools") # Only if you don't have the devtools package
devtools::install_github("ndphillips/VisualResume")
```

## My first attempts

At first, I simply took the package author's example and tried to fill in my own information in some places.

```{r, message = FALSE, warning = FALSE}
library(VisualResume)
VisualResume::VisualResume(
 titles.left = c("Derek Sollberger", "Math, Data Science, Cooking", "*Built with love in R using the InfoResume package: www.ndphillips.github.io/inforesume"),
titles.right = c("www.dsollberger.com", "dsollberger@ucmerced.edu", "Full Resume: [TBA]"),
titles.right.cex = c(2, 2, 1),
titles.left.cex = c(4, 2, 1),
timeline.labels = c("Education", "Teaching"),
timeline = data.frame(title = c("UC Berkeley", "CSU Long Beach", "UC Merced", "Coursera", "Datacamp", "UC Campus"),
                      sub = c("BA student", "MS student", "MS student", "Data Science and Data Mining", "Continuing Learning", "High School Prep"),
                      start = c(2000, 2007, 2009, 2013, 2015, 2005),
                      end = c(2005, 2009, 2011, 2016, 2017, 2005),
                      side = c(1, 1, 1, 1, 1, 0)),
milestones = data.frame(title = c("BA", "MS", "PhD"),
                        sub = c("Mathematics", "Chemistry", "Chemistry"),
                        year = c(1980, 1982, 1985)),
events = data.frame(year = c(1985, 1995, 1997, 1999, 2012),
                    title = c("Contributed to Nobel Prize winning experiment.",
                              "Honorary mention for best Chemistry teacher of the year.",
                              "Created Blue Sky, the most potent methamphetamine ever produced.",
                              "Made first $1,000,000.",
                              "White, W., & Pinkman, J. (2012). Blue Sky: A method of [...].\nJournal of Psychopharmical Substances, 1(1),.")),
interests = list("programming" = c(rep("R", 10), rep("Python", 1), rep("JavaScript", 2), "MatLab"),
                 "statistics" = c(rep("Decision Trees", 10), rep("Bayesian", 5), rep("Regression", 3)),
                 "leadership" = c(rep("Motivation", 10), rep("Decision Making", 5), rep("Manipulation", 30))),
year.steps = 2
)
```

I soon realized that I would rather organize the information in a separate spreadsheet.

```{r, message = FALSE, warning = FALSE}
library("readxl")
timelineDB <- read_excel("resumeDB.xlsx", sheet = "forTimeline")
milestoneDB <- read_excel("resumeDB.xlsx", sheet = "forMilestones")
eventsDB <- read_excel("resumeDB.xlsx", sheet = "forEvents")
```

```{r}
VisualResume::VisualResume(
 titles.left = c("Derek Sollberger", "Math, Data Science, Cooking", "*Built with love in R using the InfoResume package: www.ndphillips.github.io/inforesume"),
titles.right = c("www.dsollberger.com", "dsollberger@ucmerced.edu", "Full Resume: [TBA]"),
titles.right.cex = c(2, 2, 1),
titles.left.cex = c(4, 2, 1),
timeline.labels = c("Education", "Teaching"),
timeline = timelineDB,
milestones = milestoneDB,
events = eventsDB,
interests = list("Math Teaching" = c(rep("Statistics", 5), rep("Calculus", 10), rep("Trigonometry", 2)),
                 "Data Science" = c(rep("R", 10), rep("GIS", 2), rep("R Markdown", 5), rep("Shiny", 3)),
                 "Cooking" = c(rep("Sous Vide", 4), rep("Tapas", 8), rep("Sushi", 10))),
year.steps = 1
)
```

There were some errors what I may need to investigate later.  For now, I am going to revert back to inputting some the data manually.

```{r, message = FALSE, warning = FALSE}
VisualResume::VisualResume(
 titles.left = c("Derek Sollberger", "Math, Data Science, Cooking", "*Built with love in R using the InfoResume package: www.ndphillips.github.io/inforesume"),
titles.right = c("www.dsollberger.com", "dsollberger@ucmerced.edu", "https://github.com/dsollberger"),
titles.right.cex = c(2, 2, 1),
titles.left.cex = c(4, 2, 1),
timeline.labels = c("Education", "Teaching"),
timeline = timelineDB,
milestones = milestoneDB,
events = data.frame(year = c(2018, 2017, 2014, 2012, 2011, 2009, 2005),
                    title = c("Mentor of the Year award",
                              "Promoted to Continuing Lecturer status",
                              "Hosted UCM's first annual Data Crunch hack-a-thon",
                              "Integration Bee winner (faculty division)",
                              "Capstone Project in Hidden Markov Models",
                              "Comprehensive exams in Numerical Analysis and Nonlinear ODEs",
                              "UCB Circle K Member of the Year")),
interests = list("Math Teaching" = c(rep("Data Science", 20), rep("Bio-genomics", 15), rep("Calculus", 10), rep("Trigonometry", 5)),
                 "Data Science" = c(rep("R", 20), rep("GIS", 10), rep("R Markdown", 15), rep("Shiny", 5)),
                 "Cooking" = c(rep("Sous Vide", 15), rep("Tapas", 10), rep("Sushi", 5), rep("Meal Planning", 20))),
year.steps = 1
)
```

